\chapter{Introduction}
\label{ch:intro}

The realm of nuclear security involves many parallel efforts in
nonproliferation (verification of treaty compliance, monitoring for smuggling,
proper storage and transportation of nuclear materials), cyber security,
minimizing stocks of weaponizable materials, disaster response training, and
nuclear forensics. All of these efforts have been continually improving, but
there was a gap regarding the ability of the \gls{US} to coordinate and respond
to a nuclear incident, especially with the technical portion of nuclear
forensics: characterization and analysis. After all, the first textbook on the
topic was published in 2005 \cite{nftext_2005}. In 2006, the \gls{US} \gls{DHS}
founded the \gls{NTNFC} within the \gls{DNDO}. The mission of the \gls{NTNFC}
is to establish a robust nuclear forensics capability to attribute radioactive
materials with demonstrable proof.

There are many fields that contribute to the nuclear forensics capability, such
as radiochemical separations, material collection techniques, improving
detector technology, material library development, and identifying forensic
signatures. These needs vary based on whether the material being collected is
post-detonation (e.g., bomb debris) or pre-detonation (e.g., \gls{SNF}).  In
the pre-detonation realm, this project focuses on statistical methods to
identify correlated material characteristics, which can lead to new forensic
signatures. 


\section{Motivation}
\label{sec:motivation}

Nuclear forensics is an important aspect of deterring nuclear terrorism even
though it is not, at first glance, thought to be preventative nuclear security.
The most common defense of the field is that nuclear forensics capability
deters state actors, not terrorist organizations. While it is true that a
strong capability encourages governments to be more active in prevention of
nuclear terrorism, it can also deter the terrorist organizations as well by
increasing their chances of failure. Less destructive success tends to be more
valued than high-risk mass destruction. In addition to influencing governments
and making nuclear terrorism higher risk for organizations, nuclear forensics
can assist in cutting off certain suppliers of nuclear materials or
technologies (e.g., nuclear specialists that are only involved for financial
reasons, access to state suppliers).  Shutting off the sources builds a
concrete barrier to nuclear terrorism.  Therefore, nuclear forensics is
considered impede this form of terrorism in both tangible and abstract ways
\cite{aps_aaas_forensics}.

Following the prevention value of nuclear forensics, it is important to
understand the process of the technical portion of the investigation and how
that can be improved.  In the event of a nuclear incident, such as the
retrieval of stolen \gls{SNM} or the detonation of a dirty bomb, it is
necessary to learn as much as possible about the source of the materials in a
timely manner. In the case of non-detonated \gls{SNM}, knowing the reactor
parameters that produced it can point investigators in the right direction in
order to determine the chain of custody of the interdicted material.
Determining these parameters (e.g., reactor type, cooling time, burnup)
requires first characterizing and calculating certain isotopic ratios, chemical
compounds, or trace elements.  Both radiological methods (e.g., gamma
spectroscopy) and ionization methods (e.g., mass spectrometry) measure these
quantities. Although both measurement techniques have a multitude of techniques
within them and thus varying strengths and weaknesses, the main tradeoff is
between time/cost and amount of information gained. 

The results of these analytic techniques are then compared against existing
databases to obtain the desired reactor parameters. These databases are highly
multidimensional, and furthermore, are rife with missing data entries and
inconsistent uncertainties. Direct comparison between measurement results and a
database therefore may not yield accurate results. Thus, computational
techniques have been developed by nuclear engineers to calculate the parameters
relevant to nuclear forensics analysis \cite{weber_2006, weber_2010,
weber_2011}. Another approach with the uniqueness of requiring minimal domain
knowledge is the use of statistical methods via machine learning algorithms to
predict these characteristics or values \cite{dayman_feasibility_2013,
robel_2009, nicolaou_2006, nicolaou_2009, nicolaou_2014, jones_snf_2014,
jones_viz_2014}. These algorithms can create a model using the database entries
that enables "filling between the lines" of its entries. Additionally, having a
machine-learned model may overcome the above challenges of multidimensionality,
missing data, and irregular uncertainty.

\subsection{Needs in Nuclear Forensics}
\input{chapters/intro/forensics}
\label{sec:nfneeds}

\subsection{Contribution of Statistical Methods}
\input{chapters/intro/statlearning}
\label{sec:statscontrib}

\section{Methodology}
\label{sec:methodology}

As previously mentioned, the typical workflow of the technical portion of a
forensics investigation is to take measurements of an unknown material and
compare those measurements to databases filled with previously measured
standard materials. As this work focuses on \gls{SNF}, these measurements are
elemental, chemical, and radiological in nature.  Because creating databases
from real measurements to represent \gls{SNF} from reactor technologies from
around the world is impossible, the database in this study will be created from
high-fidelity simulations via \gls{ORIGEN} \cite{origen} within the SCALE code
system \cite{scale} for modeling and simulation. 

In the simulation and statistical learning paradigm, we need to determine how
much information to what quality is needed to train a machine-learned model;
the model must give appropriate predictions of reactor parameters given a set
of measurements from a test sample of interdicted \gls{SNF}. Thus, the space 
that the training set encompasses must be chosen carefully so as to represent 
the typical scenario for stolen \gls{SNF}.

The next step is to choose an algorithm that performs statistical learning.
Statistical learners have varied strengths and weaknesses based on what is
being predicted and how they implement optimization.  Chosen for this study are
simple regression algorithms for burnup prediction: nearest neighbor and ridge
regression.  For comparison, support vector regression is used because it is
known to handle highly dimensional data sets well.  These algorithms are
introduced in \label{sec:algs}.

After the training is complete, the results of each models' predictions must be
evaluated.  Typically, a test set is used to compare against the model created
from the training set.  The testing error can therefore be tabulated with
respect to various specifications such as the training set size, number of
features, or algorithm parameters (regularization terms, etc). These results
are broadly known as diagnostic plots and show if the algorithms' predictions
are due to good performance or bad fitting. 

After the models are evaluated using machine learning best practices, it will
be important to compare them both against each other and against other
computational forensics parameter methods. Thus, a Bayesian approach from the
field of inverse problem theory will be used to give the probability density of
the predictions so that the statistically generated predictions can be
evaluated directly against other solutions, such as optimization-based methods
or direct computations. 

Next, information reduction (within the training and/or testing data sets) must
be investigated to extend this workflow to mimic that of the real world. The
primary example investigated here is the reduction of information quality via
gamma ray detectors, as they can provide fast results.  If an algorithm could
overcome the limitations of gamma detection and still provide useful results,
this would warrant further studies and perhaps be field-applicable.

Thus, ultimately, the goal is to answer the question \textit{How
does the ability to determine forensic-relevant spent nuclear fuel attributes
degrade as less information is available?}. 

\section{Goals}
\input{chapters/intro/goals}
