\footnotesize{ This proposal would not be possible with the wisdom and patience
of my advisor, Paul Wilson. May you never suffer another student like me.  I'm
also appreciative of the CNERG community for technical and non-technical
assistance; may quiche recipes be forever shared during important phone calls.
Kelly Burton and Max Lagally have invested \textbf{much} effort into my success
and convinced me to remain on the graduate school path---more than once.  This
material is based upon work funded by the National Science Foundation Graduate
Fellowship Program, as well as the \gls{US} \gls{DHS} under Grant Award Number
2012-DN-130-NF0001.\footnote{The views and conclusions contained in this
document are those of the author and should not be interpreted as representing
the official policies, either expressed or implied, of the \gls{US} \gls{DHS}.} 

Mountains of personal support motivated me here and kept me here, which I do
not take for granted. Steven ``If you're gonna be dumb you gotta be tough''
Harrell, my chosen father, pushed me to get all my KSAs via grad school.  My
GERS friends have motivated me since the beginning, especially Jos\'e Roberto,
Richard, and Chandler.  Robin, you have been such a light in my life for over a
decade and always remind me why I came back to grad school.  And to my friends
for 15 years, Denise and April, thanks for keeping in touch despite the gaps.
Also, Ruthie, you push me to be fierce, spittin' truths and slaying your way
through life.  And my family; although enormous, some fought with and for me
during grad school.  Maurice, thanks for the help when I was struggling.  Lou,
thanks for being one of my best friends and sources of laugh lines. Liz, make
good choices.  For tirelessly encouraging my academic and personal pursuits,
I'm appreciative of my California family, Mel, Bonnie, Joelle, and Jamie. 

Finally, my Madison family has blessed me in countless ways: Shan, Krystal,
Ninja, Peter, Drax, Samira, Heather, Burnie, Brarit, Sarah, the late Otto,
James, Troy, BLou, Fetal, Corey, Martha, Matt.
}
