There can be a large number of computational tools within a given field of
study.  They are typically developed with one aspect of analysis in mind, so
one must understand the simplifying assumptions the developers made for their
purposes. Thus, choosing a computational tool is not always obvious. Thus, this
section both introduces and defends the choices for the various experimental
components.

\subsection{Fuel Cycle Simulation}

Nuclear fuel cycle studies involve tracking the material flow of nuclear fuel.
This can be anywhere from mining to waste management, or focus on a process
step anywhere in between. Fuel cycle studies are not necessarily
nuclear-specific. They can be used to evaluate, e.g., economic predictions,
environmental impact, transportation planning, etc.  In order to draw
conclusions from these studies, it is common to use a nuclear fuel cycle
simulator that tracks the quantities of interest. These allow the comparison of
different fuel types, reactor technologies, material processing steps, etc. 

As mentioned, there are simplifications researchers need to make in order to
experiment in a controlled way. Fuel cycle simulators are built for specific
needs as well and also must remove complicating factors that are generally less
relevant to the study.  For example, one tool might be suited well to
large-scale systems analysis with little nuclear physics included in the
models, and another might focus on detailed isotopics within a system to track
plutonium isotopes.

\todo{more needed?}

Because a large portion of a nuclear forensics investigation relies on
measuring isotopics, \gls{ORIGEN-ARP} \cite{origen} within the SCALE code
system was chosen for its physically detailed models. \gls{ORIGEN} calculates
time-dependent nuclide concentrations (or quantities derived from these) that
result from activation and depletion calculations. The physics (i.e., neutron
transport and decay) calculations are carried out in other SCALE modules that
solve the depletion equations.  This generates libraries for \gls{ORIGEN} that
include the probabilities of reaction (i.e., cross sections) for the system.

To obtain an \gls{SNF} recipe from a reactor simulation, \gls{ORIGEN} uses the
desired input power generation with the cross section library to calculate a
flux, the resulting depletion, and the end composition (i.e., isotopics,
nuclide vector).  Another output is decay; the composition is computed using
decay equations with nuclear data \cite{endf}. These compositions provide
source terms for other calculations, such as decay emission spectra from
neutrons, or alpha, beta, gamma rays, which use the same resource for nuclear
data. Other quantities like activity, decay heat, or radiological hazard
factors are also an option.

\gls{ORIGEN-ARP} allows users to access a wider range of simulations by
interpolating between the already calculated libraries for a wide array of
reactors instead of creating new libraries.  It is known to be validated for
\gls{LWR} \gls{SNF} \cite{lwr_valid}. Additionally, recycled \gls{SNF} in the
form of mixed oxide fuel has been benchmarked with the relevant reactors
\cite{mox_valid}.  Thus, given an initial material composition, some reactor
operation parameters, and a reactor type, one can quickly perform many
different nuclear reactor simulations and obtain \gls{SNF} recipes.

\subsection{Statistics Toolkit}

The statistics toolkit chosen for this work is scikit-learn \cite{scikit}, a
machine learning package in python.  Virtually all modern machine learning
toolkits will have acceptably fast and reliable algorithms, but the use of
python provides a platform for seamless integration of all the tools in the
workflow. 

\subsection{Computational Gamma Spectra}

Although the data modification shown later in Section \ref{sec:inforeduc} does
not use any standalone tool, the code \gls{GADRAS} \cite{gadras} developed at
Sandia National Laboratories will provide information reduction in a physically
valid manner.  Test studies will be carried out using the gamma spectra
available from \gls{ORIGEN} simulations, but the detector response will need to
be varied more than this tool can provide. Thus, given the nuclide vectors from
\gls{ORIGEN}, \gls{GADRAS} computationally generates gamma spectra from the
gamma energies and a chosen \gls{DRF}. This will enable a more robust study of 
statistical performance with respect to information reduction.

